### 2021-04-19 architecture.tex
Make the problem graph and metagraph diagrams consistent and clear
Resolves a comment from R2.

problem;
clause;
%{ rank = same;
predicate;
atom;
equality;
%}
argument;
term;
function;
variable;

@@

c0 -> t0 [label=" + "];
c1 -> t1 [label=" &ndash; "];

@@

ff [label="function|f", style=bold];
fa [label="function|a", style=bold];
fb [label="function|b", style=bold];
tfab0 [label="argument|1", style=dotted];
tfab1 [label="argument|2", style=dotted];
tfbb0 [label="argument|1", style=dotted];
tfbb1 [label="argument|2", style=dotted];
t0 -> ta;
t0 -> tb;
t1 -> tfab;
t1 -> tfbb;
tfab -> ff;
tfab -> tfab0;
tfab0 -> tfab1;
tfab0 -> ta;
tfab1 -> tb;
tfbb -> ff;
tfbb -> tfbb0;
tfbb0 -> tfbb1;
tfbb0 -> tb;
tfbb1 -> tb;
ta -> fa;
tb -> fb;

% Technical details:
%ff -> ff [dir=forward];
%fa -> fa [dir=forward];
%fb -> fb [dir=forward];
}
\caption{Graph representation of the \gls{cnf} formula $a=b \wedge f(a,b) \neq f(b,b)$}
\label{fig:GcnExample}
\end{figure}
\todo[author=R2]{There are unneeded differences in the notations used in the two figures; for example, pos/neg vs +/-, equality vs equality atom, the various (and non-specified) types of boxes around the nodes in fig. 3...}

>>>>

problem;
clause;
%{ rank = same;
predicate;
atom [label="non-equality atom"];
equality [label="equality atom"];
%}
argument;
term;
function;
variable;

@@

c0 -> t0 [label=" pos "];
c1 -> t1 [label=" neg "];

@@

ff [label="function|f"];
fa [label="function|a"];
fb [label="function|b"];
tfab0 [label="argument|1"];
tfab1 [label="argument|2"];
tfbb0 [label="argument|1"];
tfbb1 [label="argument|2"];
t0 -> ta;
t0 -> tb;
t1 -> tfab;
t1 -> tfbb;
tfab -> ff;
tfab -> tfab0;
tfab0 -> tfab1;
tfab0 -> ta;
tfab1 -> tb;
tfbb -> ff;
tfbb -> tfbb0;
tfbb0 -> tfbb1;
tfbb0 -> tb;
tfbb1 -> tb;
ta -> fa;
tb -> fb;

% Technical details:
%ff -> ff [dir=forward];
%fa -> fa [dir=forward];
%fb -> fb [dir=forward];
}
\caption{Graph representation of the \gls{cnf} formula $a=b \wedge f(a,b) \neq f(b,b)$}
\label{fig:GcnExample}
\end{figure}
